CFTP Convergence

### 2025-01-10 extensive_tests/CFTP_convergence/draft-test_CFTP_convergence.Rmd
Updating git in order to be able to pull from chile

---
title: "CFTP Convergence"
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Test for CFTP Convergence}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

```{r, out.width="0.8\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
knitr::include_graphics("Figures/CFTP_testConvergence_paramsID_01.pdf")
```

>>>>

q---
title: "CFTP Convergence"
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Test for CFTP Convergence}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

```{r, fig.align='center',  out.width='50%'}
knitr::include_graphics("Figures/CFTP_testConvergence_paramsID_01.pdf")
```

```{r, fig.align='center',  out.width='50%'}
knitr::include_graphics("Figures/CFTP_testConvergence_paramsID_02.pdf")
```

```{r, fig.align='center',  out.width='50%'}
knitr::include_graphics("Figures/CFTP_testConvergence_paramsID_03.pdf")
```

```{r, fig.align='center',  out.width='50%'}
knitr::include_graphics("Figures/CFTP_testConvergence_paramsID_04.pdf")
```

```{r, fig.align='center',  out.width='50%'}
knitr::include_graphics("Figures/CFTP_testConvergence_paramsID_05.pdf")
```

```{r, fig.align='center',  out.width='50%'}
knitr::include_graphics("Figures/CFTP_testConvergence_paramsID_06.pdf")
```

```{r, fig.align='center',  out.width='50%'}
knitr::include_graphics("Figures/CFTP_testConvergence_paramsID_07.pdf")
```

```{r, fig.align='center',  out.width='50%'}
knitr::include_graphics("Figures/CFTP_testConvergence_paramsID_08.pdf")
```

```{r, fig.align='center',  out.width='50%'}
knitr::include_graphics("Figures/CFTP_testConvergence_paramsID_09.pdf")
```

```{r, fig.align='center',  out.width='50%'}
knitr::include_graphics("Figures/CFTP_testConvergence_paramsID_10.pdf")
```
